\chapter*{Acknowledgements}
\markboth{Acknowledgements}{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
% put your text here
%\lipsum[1-2]

\bigskip
 
This thesis was a journey that would have been impossible without the help and support of many people.
\vspace{0.5cm}

First, I would like to thank my advisor Volkan Cevher. He never gave up on me despite some tumultuous steps, and fought for me to reach the end of my thesis. Few would have done this. I am also thankful that he let me pursue freely my research interests, and I am grateful to him for having built an amazing group with colleagues who are both brilliant researchers and great friends. %and I want also to thank him for building a research group of amazing colleagues and friends, both at technical and personal levels.  %brillant
% This is not enough IMO
\vspace{0.5cm}

Second, I would to express my gratitude to Prof. Alexandre Alahi, Prof. Dimitri van de Ville, Dr. Ruud van Heeswijk and Dr. Philippe Ciuciu for being part of my thesis committee and for the interest that they took in reading and evaluating my thesis, as well as for their useful suggestions. I would like to thank in particular Dr. Ruud van Heeswijk and Dr. Philippe Ciuciu for all the insight that they gave me about MRI, and Dr. Philippe Ciuciu hosting me at Neurospin, despite the visit being shortened by the start of a pandemic. I have very good memories of my short time there.

\vspace{0.5cm}

My thanks then naturally go to my friends and colleagues, who supported me during these four years and made them unforgettable. I can never repay them enough for their kindness. Thank you Baran, Paul, Ya-Ping, Ahmet, Fatih, Ali K., Kamal, Thomas, Fabian, Leello, Pedro, Igor, Chaehwan, Maria, Arda, Armin, Yura, Nadav, Grigoris, Ali R., Andrej, Luca, Stratis, Kimon, Fanghui, and all the others for your friendship and the moments that we have shared. Of course, a couple of special mentions are in order.
I want to thank Baran for introducing me to the world of MRI, and teaching me much about research and life.
I want to thank Igor for the close collaboration that we had throughout my PhD, for putting up with me through manifold argumentative and extended meetings, pesky bugs and seemingly incomprehensible experimental results, and for being so patient and supportive. I am also thankful for his healthy German honesty and for the good friend he is. %I have learned a lot from his perspective about life and research.
%[Leello acknowledged here]
I want also to thank Leello for being one of the most fun people on this planet -- I don't think that someone made me laugh more than him --  for his optimistic
%Igor comment: might find something better than optimistic
look on life, for his practical wisdom and overall for being such an amazing friend. Thank you for bringing joy and friendship to everyone around you. 
Of course, I ought to thank Gosia, the secretary of our lab, for her amazing work and efficiency in every practical matter. I suspect that she is the reason that the lab has not yet collapsed into chaos.
\vspace{0.5cm}

I am also grateful to all my friends for their support, in particular to Clément and Nathan Dupertuis, Peter Lecomte, Marion Conus and Christian Cuendet, as well as everyone from church, from the house group and from GBU. They are too numerous to be listed individually, and I feel very fortunate to be surrounded by so many kind and generous people.
\vspace{0.5cm}

Of course, without the support from my family, this thesis would not have been possible. I have been blessed by the unconditional love and encouragement from my parents, Esther and David, from my sister Myriam and her fiancé Sam, and from my brother Nicolas. I also cannot thank enough my parents-in-law, Karin and Jean-Paul.

\vspace{0.5cm}
Finally, my words turn to my best friend and amazing wife, Aline. Thank you for who you are. Thank you for your love, your support and unfailing encouragement. Without you, I could not have completed this thesis. You make every day brighter and push me to become a better man. 

%\vspace{0.5cm}
%Above all, \textit{Gloria Dei}.

\vspace{0.5cm}

\noindent\textit{Lausanne, \today}
\hfill T.~S.
